Survival Compass

### 2024-04-21 paper/paper.qmd
fixed captions

>>>>

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-two
#| fig-title: Pathologic Stage
#| fig-cap: TO DO

# install.packages
# install.packages("reshape2")
# install.packages("vcd")
# install.packages("cowplot")

# Load required libraries
library(ggplot2)
library(arrow)
library(dplyr)
library(showtext)
library(reshape2)
library(vcd)
library(patchwork)
library(cowplot)

# Create a scatter plot with trend lines - pathologic stage vs. time vs. treatment type
plot1 <- ggplot(data = analysis_data, aes(x = days_to_death, y = pathologic_stage, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +
  # Adjusted point size and transparency
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type),
              alpha = 0.3) +  # Adjust trend line transparency
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue",
                                "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Pathologic Stage",
       color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) + # Set breaks on x-axis
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14),
        # Set font to Patrick Hand and increase the size
        legend.position = "bottom", legend.text = element_text(size = 12)) +
  # Adjust legend position and text size
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5)) +
  ggtitle("Pathologic Stage vs. Time vs. Treatment Type") +
  labs(caption = "Relationship between pathologic stage, time to death, and treatment type")

# Create a scatter plot with trend lines - presence of distant metastasis vs. time vs. treatment type
plot2 <- ggplot(data = analysis_data, aes(x = days_to_death, y = presence_of_distant_metastasis, color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type),
              alpha = 0.3) +  
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue",
                                "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Presence of Distant Metastasis",
       color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), 
        legend.position = "bottom", legend.text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, size = 14)) +  
  # Adjusted size here
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5)) +
  ggtitle("Presence of Distant Metastasis vs. Time vs. Treatment Type") +
  labs(caption = "Relationship between distant metastasis, time to death, and treatment type")  
# Adjusted to caption

# Create a scatter plot with trend lines - lymph node involvement vs. time vs. treatment type
plot3 <- ggplot(data = analysis_data, aes(x = days_to_death,
                                          y = lymph_node_involvement,
                                          color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type),
              alpha = 0.3) +  
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue",
                                "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Lymph Node Involvement",
       color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), 
        legend.position = "bottom", legend.text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, size = 14)) +  
  # Adjusted size here
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5)) +
  ggtitle("Lymph Node Involvement vs. Time vs. Treatment Type") +
  labs(caption = "Relationship between lymph node involvement, time to death, and treatment type")  
# Adjusted to caption

# Create a scatter plot with trend lines - tumor size vs. time vs. treatment type
plot4 <- ggplot(data = analysis_data, aes(x = days_to_death,
                                          y = tumor_size,
                                          color = treatment_type)) +
  geom_point(size = 2.5, alpha = 0.6, shape = 19) +  
  geom_smooth(method = "lm", se = FALSE, aes(group = treatment_type),
              alpha = 0.3) +  
  scale_color_manual(values = c("Pharmaceutical Therapy, NOS" = "blue",
                                "Radiation Therapy, NOS" = "green")) +
  labs(x = "Days to Death", y = "Tumor SIze",
       color = "Treatment Type") +
  scale_x_continuous(breaks = seq(0, max(analysis_data$days_to_death),
                                  by = 500)) +
  theme_minimal() +
  theme(text = element_text(family = "patrick", size = 14), 
        legend.position = "bottom", legend.text = element_text(size = 12),
        plot.caption = element_text(hjust = 0.5, size = 14)) +  
  # Adjusted size here
  guides(color = guide_legend(title.position = "top", title.vjust = 0.5)) +
  ggtitle("Tumor Size vs. Time vs. Treatment Type") +
  labs(caption = "Relationship between tumor size, time to death, and treatment type")  
# Adjusted to caption

# Display the plots
plot1
plot2
plot3
plot4
```

# install.packages
# install.packages("reshape2")
# install.packages("vcd")

# Load required libraries
library(ggplot2)
library(arrow)
library(dplyr)
library(reshape2)
library(vcd)

# Create a ggplot2 plot for pathologic_stage and treatment_type with adjusted margins, legend, and horizontal y-axis labels
ggplot(analysis_data, aes(x = pathologic_stage, fill = treatment_type)) +
  geom_bar(position = "fill") +
  theme(axis.text.x = element_blank(), axis.text.y = element_text(angle = 0, hjust = 1)) +
  scale_fill_manual(name = "Treatment Type", values = c("Pharmaceutical Therapy, NOS" = "blue", "Radiation Therapy, NOS" = "red"))
